---
title: "Trying out R markdown"
author: "Erin Brown"
date: "16/6/2021"
output: html_document
---
- Erin Brown
- Novo Nordisk foundation Center for Basic Metabolic Research
- University of Copenhagen

# Introduction

I do not know how to use **R**, so I am taking the course *reproducibility in R*

# Methods and Results

Learning how to **markdown** is *really hard*

## Analysis
It was a **complete failure**, I had to *cheat* to get the answer

# Discussion
I should have read up more about using **R** *before* starting this course

```{r setup}
source(here::here("R/package-loading.R"))
load(here::here("data/nhanes_small.rda"))
```

```{r prettier table, echo=FALSE}
nhanes_small %>%
    filter(!is.na(diabetes)) %>% 
    group_by(diabetes, sex) %>% 
    summarise(mean_age = mean(age, na.rm = TRUE),
              mean_bmi = mean(bmi, na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(mean_age = round(mean_age,1), mean_bmi = round(mean_bmi, 1), sex = str_to_sentence(sex)) %>%
    rename("Diabetes status" = diabetes, Sex = sex, "Mean Age" = mean_age, "Mean BMI" = mean_bmi) %>% 
knitr::kable(caption = "A prettier table. Mean values of Age and BMI for each sex and diabetes status.")
```

